Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-12 paper/gen-graph-unconnected-heatmap.tex
Muck around with the graphs a bit, add some FC
More FC data

%% Thu 07 Apr 2016 11:12:12 BST

@@

  ffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffffffac88ffac88ffac88ffffffff8c72ff9f7d%
  ffac88ff8c72ff9f7dff95768b0000ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffd01d45ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ca1941ffffff%

@@

  ffac88ffffffffffffc7173effffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffc6163effffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffffffc6163dffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88%
  ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffffffffac88ffffffffffffffffffffffffffac88c7173effffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ff9f7dffffffffac88ffffffffffffffffffffffffc1133affffffffffffffffff%

@@

  ffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffffffffffffc7173fffffffffffffffffffffffffffffffffffffffffffffffffffffff%

@@

  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffac88%
  ffffffffac88ffffffffffffffffffffac88ffffffffac88ffffffffac88ffffffc6163effffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffff9576ffffffffffff%
  c91840ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffac88c4153cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffff9f7dffac88ffffffffffffffffffffac88c4143cffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7d%
  ffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffac88ffac88ff9f7dff9f7dffac88ffffffc3143b%
  ffffffffac88ffac88ffac88ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffac88%
  ffac88ffffffff9f7dffffffc11239ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffac88ffffffffffffffac88ffffffffac88ffffffffffffffffffffffffffac88%
  ffac88ffac88ffffffffac88ffffffffffffffffffffac88ffffffc4153cffffffffffffffffffffffffffffffffffff%
  ffac88ffac88ffffffffffffffffffffffffffffffffac88ffffffff9f7dff9f7dff9f7dffac88ffffffc2143bffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffac88ffac88ff9576ff9f7dff9f7dffac88%
  ffffffffffffffac88c6163dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffffffffffff%
  ffffffffffffff9576ffac88ff9576ffffffff8c72ffffffc11239ffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffff9f7dffffffffac88ffac88ffffffff9f7dff9f7dffffffff9f7dffffffff9f7dc5153cffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffac88ffac88ffac88ffffffff8c72ffffffff9576%
  ffffffff9576bd1037ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9f7dffac88ff9f7dffffff%
  ffac88ffac88ff9576ff9f7dff9f7dff9576ffac88c2133affffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88%
  ffac88ff9f7dffac88ffffffffac88ff9f7dff9f7dff9f7dff9f7dff9576ffac88ff9f7dc2133bffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ffffffffffff%
  ffffffffffffffac88ffffffffac88ffffffff9576ffac88ffac88ffffffffac88ff8c72ffffffffac88ff8c72ff8c72%
  ffffffc01239ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffff9f7dffffffff9f7dffac88ffac88ffac88ffffffffac88ff9f7dffac88%
  ff9f7dffac88ff9576ff9f7dff9f7dff9f7dc11239ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ffac88ffac88%
  ffac88ff8c72ff9576ffac88ffac88ff9f7dff9576ff846effac88ff846eff846ec4143cffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ff9f7dffac88ffffffffffffffffffffffff%
  ffac88ffac88ff9f7dff9f7dff9576ff9f7dff9f7dff9576ff9f7dff9576ff9f7dff9576ffac88ff9576ff9f7dff8c72%
  c1133affffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffac88ffffffffac88ff9f7dffac88ffac88ff9576ffac88ffac88ff846effac88ff9f7d%

>>>>

%% Tue 12 Apr 2016 14:19:16 AEST

@@

  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffff9f7dff9f7dff9f7dffac88ff9f7d%
  ff9f7dffac88ff9576ff95768b0000ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffcf1d45ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ffffffca1941ffffff%
  ffffffffac88ffffffc7173effffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffac88c7173effffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffc6163dffffffffffff%
  ffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ff9576ffffffffac88c7173fffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dffac88ffffffffffffc1133affffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffffffffac88ffac88%
  ffffffffffffffffffffffffffffffffffffc8183fffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffac88ffffffffffffffffffffffffffac88ffffffffac88ff9f7dc6163effffffffffffffffffffffff%
  c8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88%
  ffffffffffffffac88ffffffffac88c4153cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffc4143cffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffac88ffffffffac88ffac88ffffffffac88ffac88ff9f7dffac88ff9f7dffffffc3143b%
  ffffffffac88ffffffffac88ffffffffffffffffffffac88ffac88ffffffffac88ffffffffac88ffffffffffffff9f7d%
  ffac88ffffffffffffff9f7dc1133affffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffffac88ffffff%
  ffffffffac88ffac88ffffffffac88ffffffffffffffac88ffac88c4153cffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffff9576ffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88c2133affffff%
  ffac88ffffffffffffffffffffffffffffffffac88ffac88ffac88ffffffffac88ffffffffac88ffffffff9576ffac88%
  ff9576ffffffff9f7dc6163dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffff%
  ffac88ffffffffac88ffac88ffffffffac88ffac88ff846ec01239ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7d%
  ffffffffffffffffffffac88ffac88ffffffffac88ffffffff9576ffffffffac88ffac88ffffffc4153cffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffffffff9f7dffffffffffffffffffffac88ffffffffffffffffffffac88ff9f7dff9f7dffffffffffffffac88ff9f7d%
  ff9f7dffffffbd0f36ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffff9576ffffffffac88%
  ff9f7dffac88ff9576ff9f7dff9576ffffffffac88c2133affffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffac88ffffffffffffffffffffac88%
  ffac88ffffffff9f7dffffffffac88ffac88ff9576ffffffffac88ff9f7dff9576ffffffc1133affffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffff%
  ff9f7dffffffffffffffffffffac88ffffffffffffffac88ff9f7dff9576ffffffffac88ffffffff9f7dff9f7dff8c72%
  ff9f7dc01238ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%

@@

  ffffffffffffffffffffffffffffffffffffff9f7dffac88ffac88ffffffffffffff9f7dffffffff9576ffac88ffac88%
  ffac88ff9f7dff9576ff846effac88ffac88c1133affffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ff9f7dffffffffffffffac88ff9f7d%
  ffffffff9f7dff9576ff9f7dffac88ff9576ffac88ff9f7dff846eff8c72ff8c72c3143bffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ff9f7dffffffffac88ffac88ffac88%
  ffffffff9f7dff9f7dff9f7dff9f7dffac88ff9f7dffac88ffac88ffac88ff846eff9576ff9f7dff9f7dff9f7dff9576%
  c11239ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffac88ffffffffffffff9f7dffac88ffffffffffffffac88ffac88ffac88ff9576ffac88ffffffffac88%
  ff9576ff9576ff846eff846effffffbd1036ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffac88ffac88ffac88ffac88ffac88ff9576ff846eff9f7dffffffff9f7d%
  ffffffffffffff9f7dffffffff9f7dffffffff9576ff9576ffac88ffac88c01239ffffffffffffffffffffffffffffff%

@@

  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffff9576%
  ffac88ffac88ff9f7dff846effffffffac88ff846eff9576ff9576ffac88ff8c72ff9f7dff8c72ffffffff9f7dbf1138%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffff9576ffffffffac88ffffff%
  ffffffffac88ffffffffac88ffffffff9576ff9f7dffac88ff8c72ff9576ff8c72ffac88ffac88ff9f7dff9f7dffac88%
  ffffffff8c72ff846effac88c11239ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffff9f7dff9f7dffac88ffffffff9f7dff9f7dffac88ffac88ff8c72ff9f7dff9f7d%
  ff8c72ff9576ff8c72ff9f7dff8c72ff9f7dff846eff8c72ff7e6cc11239ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88ffac88ff9f7dffac88%
  ffac88ffac88ff9f7dff7e6cffac88ff9f7dffffffff9576ff9f7dff9576ff9f7dff9576ffac88fb605fc2133bffffff%
  ffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffffffac88ffffffffffffff9f7dffac88ffac88%
  ffffffffac88ffffffff846eff846eff9576ffac88ff846effffffff8c72ff9576ff9f7dff9576ff846effac88ff7869%
  ff7e6cff9576ff8c72c4153cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffff9f7dff9f7dffac88ffffffffac88ff846eff846eff9576ff7869ffffffff8c72ffffff%
  ff8c72ffac88ff8c72ff7e6cff9576ff8c72ff846eff9576c01239ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffff9f7dffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffac88ffffffffffffff9f7dffffffffac88ffac88ff9f7dffac88ff9576%
  ffac88ffffffff846eff9f7dff8c72ff846eff7e6cff9f7dff7869ff9576ff7e6cff8c72ff7e6cc1133affffffffffff%
  ffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ffffffff9f7dffffffffac88ff9f7dff9576%
  ff8c72ff9576ffac88ff7e6cffac88ff9f7dffac88ff846eff8c72ff9f7dff9576ff9576ff7367ff6f65ff846eff8c72%
  ff7e6cff7e6cc3143bffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffffffffac88ffac88ff9576ffac88ffffffffac88ffac88ff9576ff9f7dffac88ff7869ffac88ff9f7dff8c72ff7869%
  ff8c72ff9f7dff7367ff7e6cff9576ff6f65ff7e6cc6163dffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ffffffffffffffac88ffffff%
  ffffffffffffffffffffffffff9576ffffffffffffff9f7dffac88ff9f7dffac88ff9576ff9f7dffac88ff846eff7e6c%
  ff7869ff846effac88ffac88ffac88ff9f7dff7e6cffac88ff846eff7869ff8c72ff8c72c4153cffffffffffffffffff%
  ffffffffac88ffffffffac88ffac88ffac88ffffffffac88ffffffffac88ffac88ffffffffac88ff8c72ffffffffffff%
  ff8c72ff9f7dff9f7dff9576ff7869ff9f7dff7e6cff7869ff8c72ffac88ff7869ffac88ff8c72ff8c72ff7869ff7e6c%
  ff9576c4153cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ff9f7dff9f7dffffffffac88ffffff%
  ff9f7dffac88ff8c72ff8c72ff9576ffffffff9f7dffac88ff846eff7869ff9576ffffffff846eff9576ff8c72ff7869%
  ff846eff9576ff7e6cff6b63ff7e6cff8c72cb1a41ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffac88ffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffac88%
  ff9f7dff9f7dff9f7dff9576ffac88ffffffff8c72ff9f7dffac88ff8c72ff9f7dff8c72ff9576ff7e6cff7869ffac88%
  ff8c72ff9576ff7869ff846eff7e6cff6b63ffac88ff9576ff846eff9576ff8c72c8183fffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffac88ffffffffffffffffffffffffffac88ffac88ffac88ffffffffac88ff9f7dffac88%
  ffffffffffffffffffffffffffffffffac88ffac88ffffffff846effffffffffffffac88ff9f7dff7869ff8c72ff8c72%
  ff9576ff8c72ff846eff9576ff7e6cff846eff846eff7e6cff7367ff7e6cff9576ff7e6cff8c72ff9f7dff9f7dff7e6c%
  c8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffac88ffffffffffffffffffffac88ffffffffffffff9f7dffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffff9f7dff9f7dffffffffac88ff9576ffac88ffac88%
  ff9f7dffffffffac88ff846effffffffac88ff9f7dff846eff6f65ff7367ff846eff9576ff8c72ff846eff846eff7e6c%
  ff9576ff846eff8c72ff8c72ff6b63c8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ffffffffac88ffffffffffffffffffffac88ffffff%
  ffffffffffffffac88ff7e6cff846eff9576ff846eff9f7dff846eff7e6cff9f7dff7e6cff7869ff8c72ff7e6cff9f7d%
  ff846eff8c72ff9f7dffac88ff9576ff846eff8c72ff7367ff846effac88c7173effffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffac88ffac88%
  ffac88ffffffffffffffffffffac88ffac88ff9576ff9576ffac88ffac88ff9576ff9576ffac88ff9f7dff9576ff9576%
  ff9576ff7e6cff9576ff7e6cff7e6cff846eff8c72ff9576ff7869ff8c72ff7869ff7e6cfd6561fe6862ff7e6cc6163e%
  ff9f7dffffffffffffffac88ffffffffac88ff9f7dffac88ffffffffffffffac88ffac88ff8c72ffac88ff846effac88%
  ff846eff7e6cff8c72ff7e6cff7e6cff846eff8c72fd6561ff7869ff7869ff9576ff7e6cff9576ff8c72ff7e6cffffff%
  ff9576ff7869ff8c72ff7367c8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffff%
  ffffffffffffff9f7dffac88ffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ff9f7dff8c72ffac88%
  ffac88ff9f7dffffffff7e6cff9f7dffac88ff9576ff846eff7e6cfe6862ff846eff7869ff8c72ff6f65ff7367ff9576%
  ff7869ff846eff9f7dff7e6cfc6260ff9f7dff7869ff8c72ff7869cc1a42ffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffac88ffffffffac88ffffffffffffffac88ffac88ffffffffac88ffffffffac88ff9f7dffffffffac88%
  ff9f7dff9f7dffffffffac88ff8c72ff9f7dff846effac88ff846eff9f7dff846eff9576ff8c72ff7e6cff6f65ff7869%
  ff7367ff846eff7869fe6862ff9576ff7869ff7e6cff6b63ff7e6cff7e6cff9576ff846eff7869ff846ec8183fffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffac88ffffffffffffffffff%
  ff9f7dffffffffffffffac88ffac88ff9f7dff9f7dff9576ffac88ffffffffac88ff8c72ff7869ff7869ff8c72ff9576%
  ff7367ff7869ff8c72ff8c72ff7367ff846eff7869ff846eff6f65ff846eff846eff7e6cff7869ff8c72fd6561ff9f7d%
  ff9576ff846eff9f7dcb1a41ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ff8c72ffac88ffffffffffffffffffffac88ffac88ffffffffffffffac88ffac88ff9f7dffac88ffffffffac88ff8c72%
  ff9576ff8c72ff9576ff9576ff7e6cff9f7dff6f65ff7869ff6b63ff7869ff7869ff846effac88ff846eff7367ff7e6c%
  ff6b63ff7869ff6f65ff8c72ff846eff846eff6b63fe6862ca1940ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffff9f7dffffff%
  ffffffffffffffac88ffffffffffffffac88ff9f7dffffffffac88ff9f7dffac88ff9576ffffffff9f7dff9f7dffffff%
  ffac88ff9f7dffffffff9f7dff9576ff846effffffff8c72ff8c72ff9576ff6f65ff7e6cff6b63ff7e6cff846efe6862%
  ff6f65ff8c72ff6b63ff846eff7869ff8c72ff7869ff9576ff7869ff7869fe6862ff6f65ff6f65d42148ffffffffffff%
  ffffffffffffffffffffac88ffffffffac88ffffffffac88ffffffff9f7dffffffffac88ffac88ff9f7dff9576ffac88%
  ffac88ffac88ffffffff8c72ff9f7dff9f7dffac88ff8c72ff8c72ff9f7dffac88ff846eff9576ff8c72ff7e6cff7367%
  ff7367ff7e6cff7e6cff6f65ff7e6cff7367ff7869ff7e6cff7869ff8c72ff7367ff846eff8c72ff7869ff7e6cff7367%
  ff6b63ff9576d11e46ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffac88ffffffffffffffffffff9f7dffffffffac88ffac88ffac88ffac88ffac88ffffff%
  ffac88ffac88ffffffff9f7dffac88ff9576ff846eff9f7dffac88ff9f7dffac88ff9f7dff9f7dffac88ff9f7dff9f7d%
  ff8c72ff7869ff7869ff7e6cff846efd6561fd6561ff6f65fe6862ff7869ff7367ff8c72ff7869ff7367ff7869ff8c72%
  fe6862ff8c72ff846eff7367ff6b63ff846eff7e6cd11e46ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffac88ffac88ffffffffac88ffac88ffac88ffffffffac88ffac88ff9f7dffac88ffac88ffffffffac88ff9576ffffff%
  ff9f7dff8c72ff9f7dff8c72ff8c72ff9f7dff7869ff7e6cff846eff6b63ff846eff6b63fb605fff7e6cff9576ff8c72%
  ff7869ff7869ff7e6cff846eff6f65ff7869ff7869ff6b63ff6f65ff9f7dff7367ff846ed21f47ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffff9576ffac88ffac88ffac88ffac88ffac88ff9f7dffac88%
  ffffffffac88ffac88ffffffffffffff9f7dffac88ff9576ff6b63ff7e6cff9f7dff7869ff7e6cff9576fe6862ff846e%
  fd6561ff6b63ff6f65ff846efe6862ff6b63ff9576ff6b63fd6561ff846eff9576ff8c72ff846eff8c72ff7e6cff7869%
  ff7869cd1c43ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ff9576ff9f7d%
  ff9f7dff9576ffac88ffffffffac88ff9576ffac88ffffffff9f7dffffffffffffff8c72ff9576ff9576ff846eff7869%
  ff9576ff9576ff6f65ff7e6cff6f65ff7367ff846eff7869ff6f65ff846eff7869ff6f65ff8c72ff9f7dff6f65ff7367%
  ff6f65ff6f65ff8c72ff9f7dff7e6cff846ed01e45ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ffffffffffffffffffffac88ff9f7d%
  ffac88ffac88ff9f7dffac88ffffffff9f7dff9f7dff8c72ffffffff7e6cff9576ff8c72ffac88ff9f7dff9576ff9576%
  ff8c72ffffffff9f7dff846eff6b63fe6862ff7e6cfa5e5ffd6561ff6f65ff7869fd6561ff6f65ff6f65ff9576ff9576%
  ff6f65ff846eff7367ff846eff6f65ff7e6cfd6561ff6f65fd6561ff846eff7e6cd52248ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ffffffffac88%
  ffac88ffffffffffffffffffffac88ffac88ff9f7dffffffffac88ff9f7dffffffffac88ff9f7dffac88ff9576ffac88%
  ff8c72ff9f7dff9576ffac88ff9f7dff846eff8c72ff846eff7367ff7e6cff6f65ff8c72ff846eff6b63fe6862f95c5e%
  ff7367ff6f65ff846eff9f7dff7e6cff6f65ff7e6cff7869fe6862ff7e6cff7869ff9f7dfe6862ff846eff846eff7e6c%
  d72549ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffac88ffffffff9576ffac88ffffffff9576ffffffffac88ff8c72ff9576ff846effffff%
  ffffffff6f65ffac88ffffffff9f7dff9576ff9f7dff9f7dff846eff6f65ff7367ff7869ff846eff846eff8c72ff7367%
  fc6260ff7e6cfe6862ff6f65ff6b63ff6f65ff7367ff6b63fe6862ff6b63ff846eff6f65ff7869ff7869ff7367ff7869%
  ff7869ff6f65ff7e6cff7367fe6862d72549ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ff9f7dffac88ffac88ffac88ff9f7dff7e6cffac88%
  ff9f7dffac88ffac88ffffffff6f65ff9576ff7367ffac88ff846effac88ff846eff7e6cff7e6cff7e6cff6f65ff7367%
  ff8c72fe6862ff7869ff7869fb605fff7e6cff6f65ff7367ff7367fc6260fc6260ff846eff7869ff7367ff7869ff7367%
  ff846efd6561ff7869ff846eff6b63ff7367ff7869ff7367ff846eff7367d62449ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffac88ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ff9f7dff8c72ff9f7dffac88ff8c72ffac88ff9576ff8c72ff9576ff8c72ff9576ff9576ff8c72%
  ff9f7dff9576ff8c72ff7869ff7869ff6b63fd6561ff6b63ff7367ff7367ff7869ff7367ff7869fe6862fb605fff6b63%
  ff6b63fd6561ff7869fe6862ff7367ff6f65ff6f65ff7367fe6862ff6b63ff6f65fe6862ff9576ff9f7dff7e6cd62449%

@@

  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ff9f7d%
  ffac88ffac88ffffffffffffffac88ffac88ffac88ffac88ffffffff846eff9f7dff8c72ff8c72ff9576ff7869ff8c72%
  ff7367ff9f7dff8c72ff7367ff6b63ff846eff6f65ff9576ff7e6cff8c72ff7367ff6f65ff7e6cff6f65ff6b63ff6b63%
  ff6f65fe6862fd6561ff7869fe6862ff6f65f7585dfb605ffb605fff6f65ff7367fd6561ff6f65ff6f65ff7367ff8c72%
  ff7367ff9f7dff7e6cff8c72db2a4cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffac88ff9f7dffffffffac88ffffffffffffffac88ff8c72ffffffffac88ff7e6cffac88ff8c72ff9f7dff8c72%
  ffac88ff8c72ff7367ff9576ff9576ff846eff9f7dff8c72ff6b63ff846efd6561ff846efe6862ff7869fc6260ff6f65%
  ff7869ff6f65ff6f65ff6b63ff6f65fb605ffc6260ff7367fd6561f95c5eff6f65ff7367ff7367ff7367ff6f65fb605f%
  f6545cff7869ff7869ff6b63ff6b63fc6260fc6260ff8c72ff7367db2a4cffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffff9576ff9f7d%
  ffac88ff846effac88ffac88ffac88ff7e6cff9f7dff7869ff846eff8c72ff846eff7367ff8c72ff7869ff7e6cff7869%
  ff7e6cff8c72ff9f7dff7e6cff8c72ff6b63ff6f65fe6862ff7367fa5e5fff846efc6260ff7869ff6b63ff6b63ff7367%
  fe6862ff7869ff6b63fe6862f95c5ef95c5eff7869ff6b63fe6862ff6f65fe6862ff7869ff846eff7e6cda294bffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ffac88ffac88ffffffffffffffffff%
  ffac88ffac88ffac88ff9576ffac88ff7e6cff9f7dff846eff9576ff8c72ff7367ff846eff846eff6b63ffac88ff7e6c%
  ff7869ffac88ff6b63fd6561ff7367fd6561fd6561ff6b63fa5e5ff95c5eff6b63ff7869fc6260ff6f65ff6b63ff6f65%
  fe6862fc6260ff7367fb605ff85a5df7565cff6b63ff6f65ff6b63fc6260fe6862fd6561ff7367fb605fff6f65ff7367%
  ff7869fe6862ff6f65de2d4dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffac88ffffff%
  ffac88ffac88ffac88ff9f7dffac88ff9f7dffac88ffac88ff846eff9576ffac88ff9f7dff7e6cff6b63ff7e6cff846e%
  ff6f65ff7e6cfd6561ff6f65ff6b63f95c5efe6862fd6561ff9576fc6260ff6b63ff6f65ff7367fe6862ff7367fc6260%
  f85a5df95c5efc6260f95c5efc6260fa5e5fff6f65ff7367fe6862fa5e5fff6f65f7565cfd6561ff7367fb605ff85a5d%
  fe6862ff7367fd6561ff7367ff846eff9576ff7869ff7869e1324fffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88ffac88ffffffff8c72ffac88ff9576%
  ff9576ff9f7dff7e6cff9f7dffac88ff9f7dff9f7dffac88ff9f7dff9f7dffffffff8c72ffffffffffffff9f7dffac88%
  ff9f7dff9576ff9f7dff9f7dffffffff9f7dffffffff9576ff9f7dffac88ff9f7dff9576ff9f7dff8c72ff9f7dff7367%
  ff9f7dff846eff7869ff7869ff7869ff9576ff7367f7585df7585dfe6862ff6f65ff7869fe6862fb605fff6b63ff9576%
  fe6862fd6561f95c5efa5e5ff7585dfc6260f7585df5515bf14958f6545cf95c5ef95c5ef14958ff6f65f6545cf7585d%
  f95c5ef85a5dfe6862ff7e6cff7869fe6862ff6f65ff6b63ff7869ff6b63ff6b63ff6f65ff6b63e1324fffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff7e6cff846eff6b63ff7367%
